---
title: "SMDS Homework - Block 5"
author: "E. Fabrici, V. Plesco, L. Arrighi | Group 'D'"
date: "22th June 2020"
output:
  html_document:
    toc: yes
  beamer_presentation:
    highlight: tango
  include: null
  ioslides_presentation:
    highlight: tango
  pdf_document:
    highlight: tango
    keep_tex: yes
    toc: yes
  slide_level: 2
  slidy_presentation:
    fig.height: 3
    fig.width: 4
    highlight: tango
header-includes:
- \usepackage{color}
- \usepackage{graphicx}
- \usepackage{grffile}
- \definecolor{Purple}{HTML}{911146}
- \definecolor{Orange}{HTML}{CF4A30}
- \setbeamercolor{alerted text}{fg=Orange}
- \setbeamercolor{frametitle}{bg=Purple}
institute: University of Trieste, SISSA, ICTP, University of Udine
graphics: yes
fontsize: 10pt
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center', warning=FALSE, message=FALSE, fig.asp=0.625, dev='png', global.par = TRUE, dev.args=list(pointsize=10), fig.path = 'figs/')
library(MASS)
```

```{r setup, include=FALSE}
library(knitr)
local({
  hook_plot = knit_hooks$get('plot')
  knit_hooks$set(plot = function(x, options) {
    paste0('\n\n----\n\n', hook_plot(x, options))
  })
})
```

# Homeworks {.tabset}

## Used libraries {.tabset}

```{r}
library(ggplot2)
library(lattice)
library(DAAG)
```



## DAAG EXERCISES {.tabset}

### Chapter x {.tabset}

#### Exercise x

Text here.

##### Solution

```{r Test_ex, code = readLines("src/Test_ex.R"), echo=TRUE}
```

##### Observations

Observations.

##### Conclusion

Conclusions.



## CASI EXERCISES {.tabset}

### Chapter x {.tabset}

#### Exercise x

Text here.

##### Solution

```{r Test_ex, code = readLines("src/Test_ex.R"), echo=TRUE}
```

##### Observations

Observations.

##### Conclusion

Conclusions.



## CS EXERCISES {.tabset}

### Chapter x {.tabset}

#### Exercise x

Text here.

##### Solution

```{r Test_ex, code = readLines("src/Test_ex.R"), echo=TRUE}
```

##### Observations

Observations.

##### Conclusion

Conclusions.

